### 2025-02-25 scripts/Paper-analysis.Rmd
pangenome statistics plot

>>>>

Make a plot of these results, including information on PTU pangenome size:

```{r}
ptu_for_plotting = ptu %>% pivot_longer(cols=c("n.core", "n.others"))
ptu_for_plotting$name = ordered(ptu_for_plotting$name,
                                levels=c("n.others", "n.core"))
ggplot(ptu_for_plotting, aes(PTU, value, fill=name))+
  geom_bar(stat="identity", position="stack")+
  coord_flip()
# Want average size of the PTU as well...
